Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-28 cogsci2016/paper.tex
intro

	Active curiosity-driven learning models	\cite{santucci2013}.
	Modelling work has shown that developmental trajectories could emerge from the curiosity-driven active learning of sensorimotor models \cite{oudeyer_what_2007} \cite{moulin-frier_self-organization_2014}.
	Details on those models.
	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
	1) the intrinsic motivation to explore as a self-regulation of the learning growth of complexity, and 
	2) the structure of the representation used to encode sensorimotor experience.	
	[TODO]A few words on those hypothesis: how.
	However, we do not study some other important factors of the development of tool use: the autonomous building and evolution of the hierarchy of models but we consider it given to a learning agent.
	We also do not address the question of the role of social guidance.

	IAC series of architectures and Explauto framework: previous architectures \cite{baranes_active_2013}.
	We will study aspects of these hypothesis leveraging and extending models of curiosity-driven learning of sensorimotor models to the exploration of hierarchies of sensorimotor models.
	In hierarchies of sensorimotor models, one of the sensory spaces (e.g. the position of the hand) can be used as a motor space by another higher-level model to explore other sensory spaces.
	More details on experiments: strategic learning.

@@

			\begin{figure}[t]
				\center
				\input{include/F.tikz}
				\vspace{-0.25cm}
				\input{include/H1.tikz}
				\vspace{-0.5cm}
				\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
				\label{Architectures}					
			\end{figure}

>>>>

	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
	1) the intrinsic motivation to explore as a self-regulation of the learning growth of complexity, and 
	2) the structure of the representation used to encode sensorimotor experience.	
	Indeed, curiosity-driven learning models with an intrinsic motivation towards situations yielding a high learning progress 
	have shown that developmental trajectories could emerge from the active learning of sensorimotor mappings, in very different settings.
	In the Playground Experiment \cite{oudeyer_what_2007}, a quadruped robot learned how to use its motor primitives to interact with the items of an infant play mat and a robot peer.
	Also, in a study of the self-organization of vocalizations \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
	In both studies, developmental trajectories of increasing complexity are emerging from learning, with both regularities in developmental steps and diversity.
	The diversity comes from different mechanisms: random generation in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
	In those models, the agent learns only one mapping that relates a motor space to a sensory or task space. 
	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent task spaces should be available to the agent
	as for instance complex actions with tools could make use of previously learned parameterized interaction with the tool.

	We will thus study aspects of the hypothesis leveraging and extending previous models of curiosity-driven learning.
	We will define hierarchies of sensorimotor models that structure the sensory space to reflect the interaction of the different items of the environment.
	In such hierarchies of models to explore, different exploration choices are available to the agent at each learning iteration: which model to explore, and how to explore that model.
	This problem is an instance of strategic learning \cite{nguyen2012}, 
	where different outcomes and strategies are available and the agent has to learn which strategies are useful for which outcomes. 
	We will define and compare several strategies based on active learning to solve this problem.

	Setup: architecture, model babbling, arm

	However, we do not study some other important factors of the development of tool use.
	We consider the hierarchy of models given to the agent and do not study its autonomous building and evolution during developmental stages.
	Also, social guidance with imitation and mimicry is of central importance for the development of tool use in infants but we do not address the question
	of its modeling in this paper nor the interplay and tradeoff between social learning and self-exploration.
	Another important feature of young infants' learning of tool use is the need to adapt to a developing body and to the maturation of vision during ontogenetic development, 
	but here we consider motor control and sensory perception steady over the simulated learning time span.

@@

			%\begin{figure}[t]
				%\center
				%\input{include/F.tikz}
				%\vspace{-0.25cm}
				%\input{include/H1.tikz}
				%\vspace{-0.5cm}
				%\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
				%\label{Architectures}					
			%\end{figure}
